---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(health)
```

# health

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/danielvartan/health/workflows/R-CMD-check/badge.svg)](https://github.com/danielvartan/health/actions)
[![Codecov test coverage](https://codecov.io/gh/danielvartan/health/branch/main/graph/badge.svg)](https://codecov.io/gh/danielvartan/health?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)
<!-- badges: end -->

## Overview

`health` is an R package package that contains all my (Daniel Vartanian) health data. It represents a personal project that aims to monitor my body's expression over time and create a free public record for posterity.

## Installation

`health` is still at the [experimental](https://lifecycle.r-lib.org/articles/stages.html#experimental) stage of development. That means that people can use the package and provide feedback, but it comes with no promises for long term stability.

You can install `health` from GitHub with:

``` {r, eval = FALSE}
# install.packages("pak")
pak::pkg_install("danielvartan/health")
```

## Health records

You can find the processed data (tidied, validated, and transformed version) in the `./data/` folder. The raw data is stored in the `./inst/extdata/` folder.

I try to update this repository at least once a year. Here's a list of all the health data present to date.

### Actigraphy

* 2019-10-31 - 2019-12-10 (40 days) (Device: [ActTrust 1](https://www.condorinst.com.br/acttrust/))
* 2021-04-24 - 2021-05-30 (36 days) (Device: [ActTrust 1](https://www.condorinst.com.br/acttrust/))

## License

[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/licenses/MIT)
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

This package and the accompanying data can be used freely, __with the exception of uses that end up harming myself or others__. The code is under the [MIT license](https://opensource.org/licenses/mit/) and the data is under the [Attribution 4.0 International license (CC BY 4.0)](https://creativecommons.org/licenses/by/4.0/).

For questions regarding this repository, send an e-mail to [danvartan@gmail.com](mailto:danvartan@gmail.com).

## Citation

If you use `health` in your research, please consider citing it. I put a lot of work into the collection, analysis and storage of this data, in addition to the work of building and maintaining a free and open-source R package. You can find the `health` citation below.

```{r}
citation("health")
```
